Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2017-12-23 paper-ieee-trans.tex
Update paper-ieee-trans.tex

\begin{IEEEbiography}{Doina Cristina Duma}
Biography text here.
\end{IEEEbiography}

>>>>

\begin{IEEEbiography}\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/cris_foto_good}}]{Doina Cristina Duma}
is the leader of the Distributed Systems group at the INFN National Center (CNAF), providing the core operational support for the INFN-wide Grid infrastructure and for the CNAF Cloud infrastructure. She has a long experience in managing distributed e-infrastructures, being involved since 2003 in major European projects such as DataGrid, EGEE (I, II, III), EGI-Inspire and EGI-Engage. She was the Release Manager of the EMI (European Middleware Initiative) and INDIGO - DataCloud European project project and having as main responsibilities to manage all release activities, including release planning, building, deploying, reporting, establishing and maintaining the overall release timeline and milestones. She is now the leader of the WP3 – “Software Lifecycle Management, Pilot Infrastructures & Exploitation”
of the eXtreme - DataCloud European project and leader of the WP3.2 - "Software quality assurance, release, maintenance and support" of the DEEP-HybridDataCloud.
\end{IEEEbiography}
